---
title: "URP Final Project"
author: "Susan Cheng"
date: "2025-04-20"
output: html_document
---

```{r message=FALSE}
#set path
setwd("/Users/susancheng/Desktop/URPfinal")

#install.packages('tidyverse')
library(tidyverse)
library(tidycensus)
library(sf)
library(tigris)

#html reading
library(rvest)
library(dplyr)
library(stringr)
library(readr)

#read screenshots
library(tesseract)
library(magick)
library(dplyr)
library(tibble)

#google api
library(httr)
library(jsonlite)

#create map
library(leaflet)
library(sf)
library(RColorBrewer)

```


Cleaning Fantuan Food Places HTML
```{r}
neighborhood_pattern <- "(?i)\\((.*?brooklyn.*?|BK|flushing|elmhurst|chinatown|manhattan downtown|grand st|lafayette)\\)"

fantuan_html <- function(file_path, neighborhood_label) {
  page <- read_html(file_path)

  #get name of establishment
  orig_names <- page %>%
    html_nodes(".info .name") %>%
    html_text(trim = TRUE)
  
  #filter data to only include est in selected neighborhoods
  filtered_names <- orig_names[str_detect(orig_names, neighborhood_pattern)]
  
  #clean name to remove beginning promo and end neighborhood
  clean_names <- filtered_names %>%
    str_remove("^((0\\.01 Sale|\\$?\\d+(-\\$?\\d+)?%?\\s*OFF|\\d+%?)\\s*\\|\\s*)") %>%
    str_remove("\\s*\\([^\\)]*\\)") %>%
    str_trim()
    
  #output dataframe
  tibble(
    Original = filtered_names,
    Cleaned = clean_names,
    Neighborhood = neighborhood_label
  )
}
```


Fantuan Neighborhood HTML to Database
```{r}
flushing <- fantuan_html("flushingfood.html", "Flushing")
elmhurst <- fantuan_html("elmhurstfood.html", "Elmhurst")
chinatown <- fantuan_html("chinatownfood.html", "Chinatown")
sunsetpark <- fantuan_html("sunsetparkfood.html", "Sunset Park")

#combine into one dataframe
all_data <- bind_rows(flushing, elmhurst, chinatown, sunsetpark)

#save to CSV
write_csv(all_data, "fantuan_restaurants.csv")

#print dataframe summary
all_data %>%
  count(Neighborhood, sort = TRUE) %>%
  print()
```


Hungry Panda Screenshot Text Scraping
```{r}
# ocr_engine <- tesseract("chi_sim")
# image_folder <- "hungrypanda"
# image_files <- list.files(image_folder, full.names = TRUE, pattern = "\\.(jpg|jpeg|png)$")
# 
# #extract text
# results <- lapply(image_files, function(file) {
#   img <- image_read(file)
#   text <- ocr(img, engine = ocr_engine)
#   tibble(File = basename(file), RawText = text)
# })
# 
# #combine into dataframe
# ocr_data <- bind_rows(results)
# write.csv(ocr_data, "hungrypanda_text.csv", row.names = FALSE)

```


Hungry Panda Text to Database
```{r}
# assign_neighborhood <- function(filename) {
#   num <- as.numeric(gsub("\\D", "", filename))
#   if (num <= 5070) {
#     return("Flushing")
#   } else if (num <= 5084) {
#     return("Elmhurst")
#   } else if (num <= 5136) {
#     return("Sunset Park")
#   } else {
#     return("Chinatown")
#   }
# }
# ocr_data$Neighborhood <- sapply(ocr_data$File, assign_neighborhood)
# 
# #text into lines
# expanded <- ocr_data %>%
#   mutate(Lines = strsplit(RawText, "\n")) %>%
#   tidyr::unnest(Lines) %>%
#   mutate(Business_Name = str_trim(Lines)) %>%
#   filter(nchar(Business_Name) > 2) %>%
#   select(Business_Name, Neighborhood)
# 
# #filter non business words
# non_name_keywords <- c(
#   "分钟", "距离", "评分", "红包", "优惠", "下单", "折", "热销", "配送", "商家", "元", "自取", "专送", 
#   "可取", "代金券", "秒", "爆品", "店", "已售", "点餐", "起送", "欢迎", "限时", "券",
#   "限量", "专属", "抢购", "服务", "套餐", "价格", "活动", "订单", "人", "热卖", "推荐", "满减", "满"
# )
# non_name_pattern <- paste(non_name_keywords, collapse = "|")
# 
# #set up business names
# final_hp <- expanded %>%
#   filter(
#     !str_detect(Business_Name, non_name_pattern),
#     str_detect(Business_Name, "^[\\u4e00-\\u9fa5A-Za-zA-Z0-9·\\s\\-\\.]+$"),
#     str_length(Business_Name) > 2
#   ) %>%
#   distinct()
# 
# write.csv(final_hp, "hungrypanda_restaurants.csv", row.names = FALSE)

```


Combine Both Databases
```{r}
fantuan <- read_csv("fantuan_restaurants.csv")
hungrypanda <- read_csv("hungrypanda_restaurants.csv")

fantuan_clean <- fantuan %>%
  select(Business_Name = Cleaned, Neighborhood) %>%
  mutate(Source = "Fantuan", Level = 1)

hungrypanda_clean <- hungrypanda %>%
  select(Business_Name, Neighborhood) %>%
  mutate(Source = "HungryPanda", Level = 1)

combined <- bind_rows(fantuan_clean, hungrypanda_clean)

write_csv(combined, "all_restaurants.csv")

combined %>%
  count(Neighborhood, sort = TRUE) %>%
  print()

```


Google API Geocode
```{r}
api_key <- "redacted"

#all restaurants
restaurants <- read_csv("all_restaurants.csv")

#geocode restaurants
`%||%` <- function(a, b) if (!is.null(a)) a else b

geocode_place <- function(name, neighborhood) {
  query <- paste(name, neighborhood, "New York")
  url <- "https://maps.googleapis.com/maps/api/place/textsearch/json"
  res <- GET(url, query = list(query = query, key = api_key))
  
  text_content <- content(res, as = "text", encoding = "UTF-8")
  json <- tryCatch(fromJSON(text_content), error = function(e) NULL)
  
  if (!is.null(json) && json$status == "OK" && !is.null(json$results) && is.data.frame(json$results) && nrow(json$results) > 0) {
    result <- json$results[1, ]
    return(tibble(
      Business_Name = name,
      Neighborhood = neighborhood,
      Address = result$formatted_address %||% NA,
      Latitude = result$geometry$location$lat %||% NA,
      Longitude = result$geometry$location$lng %||% NA,
      Geocode_Status = "Success"
    ))
  } else {
    return(tibble(
      Business_Name = name,
      Neighborhood = neighborhood,
      Address = NA,
      Latitude = NA,
      Longitude = NA,
      Geocode_Status = "Failed"
    ))
  }
}

#geocode rows
geocoded_all <- bind_rows(lapply(1:nrow(restaurants), function(i) {
  Sys.sleep(0.5)
  geocode_place(restaurants$Business_Name[i], restaurants$Neighborhood[i])
}))

#track failed geocodes
geocoded_success <- geocoded_all %>% filter(Geocode_Status == "Success") %>%
  distinct(Business_Name, Latitude, Longitude, .keep_all = TRUE)

geocoded_failed <- geocoded_all %>% filter(Geocode_Status == "Failed")


#csv files for both
write_csv(geocoded_success, "geocoded_restaurants.csv")
write_csv(geocoded_failed, "geocode_failed.csv")

#print results
cat("\n✅ Geocode Success Counts by Neighborhood:\n")
print(geocoded_success %>% count(Neighborhood, sort = TRUE))

cat("\n❌ Total Failed Geocodes:", nrow(geocoded_failed), "\n")

```


Level 2 & 3 Markers of Community Geocode
```{r}
api_key <- "AIzaSyCDT9A2o4bJ3k0--cXcINWjzXUuMgtiqwg"

#neighborhoods and L2 & L3 definers
neighborhoods <- c("Flushing, NY", "Chinatown Manhattan, NY", "Elmhurst, NY", "Sunset Park, NY")

l2_terms <- c(
  "Chinese supermarket", "Chinese grocery store", "Chinese temple", "Chinese church",
  "Chinese senior center", "Chinese community center", "Chinese association", 
  #"Chinese gathering park", "Chinese tai chi park", "Mahjong park", "Flushing Kissena Park", "Columbus Park", "Sunset Park Chinese community",
  "华人超市", "华超", "中国超市", "华人杂货店", "華人寺庙", "佛堂", "佛教中心", "华人教会", "基督教堂",
  "华人老人中心", "老人日托", "华人社区中心", "华侨会馆", "同乡会", "侨团", "公所"
  #"公园", "广场舞", "太极", "麻将", "下象棋", "公园唱歌", "公园戏曲", "华人公园", "华人聚集地", "老人聚集地", "带孩子玩", "社区活动公园"
)


l3_terms <- c(
  "Chinese bank", "Chinese real estate", "Chinese school", "Chinese media", "Chinese newspaper",
  "华人银行", "中资银行", "中国银行", "华人地产", "房产中介", "房地产公司",
  "中文学校", "华人学校", "补习班", "华人媒体", "中文报纸", "华人日报", "星岛日报"
)


#search
search_places <- function(keyword, location, level) {
  url <- "https://maps.googleapis.com/maps/api/place/textsearch/json"
  res <- GET(url, query = list(query = paste(keyword, location), key = api_key))
  text <- content(res, as = "text", encoding = "UTF-8")
  json <- tryCatch(fromJSON(text), error = function(e) NULL)

  cat("🔍", keyword, "|", location, "| Status:", json$status, "\n")

  if (!is.null(json) && json$status == "OK" && !is.null(json$results) && nrow(json$results) > 0) {
    df <- json$results

    tibble(
      Business_Name = df$name,
      Address = df$formatted_address,
      Latitude = df$geometry$location$lat,
      Longitude = df$geometry$location$lng,
      Keyword = keyword,
      Neighborhood = location,
      Level = level
    )
  } else {
    tibble()
  }
}


#loop for L2 & L3
run_queries <- function(keywords, level) {
  bind_rows(lapply(neighborhoods, function(n) {
    bind_rows(lapply(keywords, function(k) {
      Sys.sleep(0.5)
      search_places(k, n, level)
    }))
  }))
}

l2_results <- run_queries(l2_terms, 2)
l3_results <- run_queries(l3_terms, 3)


#csv files
all_results <- bind_rows(l2_results, l3_results)
write_csv(all_results, "googleresults.csv")

#print results

results_summary <- all_results %>%
  group_by(Neighborhood, Level) %>%
  summarise(Count = n(), .groups = "drop") %>%
  arrange(desc(Neighborhood), Level)

print(results_summary)

```


Chinese Population Setup
```{r}
census_api_key("5b88206d026d7cbdb6150604229dc66a9815f61b", install = TRUE)
readRenviron("~/.Renviron")
```

NTA Neighborhood Shapefile
```{r}
nta <- st_read("NTA2020.geojson") %>%
  st_transform(crs = 4326)
```

GeoJSON L1, L2, L3
```{r}
#load files
l1 <- read_csv("geocoded_restaurants.csv")
l23 <- read_csv("googleresults.csv")

#convert to sf
l1_sf <- st_as_sf(l1, coords = c("Longitude", "Latitude"), crs = 4326)
l23_sf <- st_as_sf(l23, coords = c("Longitude", "Latitude"), crs = 4326)

#split by level
l2_sf <- l23_sf %>% filter(Level == 2)
l3_sf <- l23_sf %>% filter(Level == 3)

#keep only results within NYC
l2_sf_clean <- l2_sf[apply(st_intersects(l2_sf, nyc_boundary, sparse = FALSE), 1, any), ]
l3_sf_clean <- l3_sf[apply(st_intersects(l3_sf, nyc_boundary, sparse = FALSE), 1, any), ]

#save GeoJSONs
st_write(l1_sf, "L1.geojson", delete_dsn = TRUE)
st_write(l2_sf_clean, "L2.geojson", delete_dsn = TRUE)
st_write(l3_sf_clean, "L3.geojson", delete_dsn = TRUE)
```


Chinese Population
```{r}
total_pop <- get_acs(
  geography = "tract",
  variables = "B02001_001",
  state = "NY",
  county = c("Bronx", "Kings", "New York", "Queens", "Richmond"),
  geometry = TRUE,
  year = 2021
)

chinese_pop <- get_acs(
  geography = "tract",
  variables = "B02018_007",
  state = "NY",
  county = c("Bronx", "Kings", "New York", "Queens", "Richmond"),
  geometry = TRUE,
  year = 2021
)

pop_data <- total_pop %>%
  select(GEOID, total = estimate, geometry) %>%
  left_join(
    chinese_pop %>% st_drop_geometry() %>% select(GEOID, chinese = estimate),
    by = "GEOID"
  ) %>%
  mutate(chinese = ifelse(is.na(chinese), 0, chinese),
         chinese_pct = (chinese / total) * 100)

```


Pop by neighborhood
```{r}
nta <- st_transform(nta, crs = st_crs(pop_data))

joined <- st_join(pop_data, nta, join = st_intersects)

nta_chinese_pct <- joined %>%
  group_by(NTAName) %>%
  summarise(
    total_pop = sum(total, na.rm = TRUE),
    chinese_pop = sum(chinese, na.rm = TRUE)
  ) %>%
  mutate(chinese_pct = (chinese_pop / total_pop) * 100) %>%
  arrange(desc(chinese_pct))

st_write(nta_chinese_pct, "nta_chinese_percent.geojson", delete_dsn = TRUE)

```

Chinatown transit score
```{r}
transit_scores <- tibble::tibble(
  Neighborhood = c("Flushing", "Elmhurst", "Sunset Park", "Chinatown Manhattan"),
  Transit_Score = c(5, 3, 4, 5)
)

```


Chinatown Connectivity Index (CCI)
```{r}
cci_inputs <- tibble(
  Neighborhood = c("Flushing", "Elmhurst", "Sunset Park", "Chinatown Manhattan"),
  
  L1 = c(695, 72, 416, 177),
  L2 = c(283, 299, 286, 216),
  L3 = c(208, 194, 158, 176),
  
  Chinese_Pop_Pct = c(75.7, 21.0, 18.1, 21.5),
  
  Transit_Score = c(5, 3, 4, 5)
)

```

Normalize CCI
```{r}
normalize <- function(x) {
  (x - min(x)) / (max(x) - min(x))
}

cci_normalized <- cci_inputs %>%
  mutate(
    L1_norm = normalize(L1),
    L2_norm = normalize(L2),
    L3_norm = normalize(L3),
    Pop_norm = normalize(Chinese_Pop_Pct),
    Transit_norm = normalize(Transit_Score)
  )

cci_final <- cci_normalized %>%
  mutate(
    CCI = L2_norm * 0.35 +
          L3_norm * 0.25 +
          L1_norm * 0.20 +
          Pop_norm * 0.10 +
          Transit_norm * 0.10
  ) %>%
  arrange(desc(CCI))

cci_final %>%
  select(Neighborhood, CCI) %>%
  arrange(desc(CCI))

```


Create Map
```{r}
nta_data <- st_read("nta_chinese_percent.geojson")
l1 <- st_read("L1.geojson")
l2 <- st_read("L2.geojson")
l3 <- st_read("L3.geojson")
# mta_lines <- st_read("official_transit.geojson")
dollar_vans <- st_read("shadowtransit.geojson")

# Color scale
pal <- colorNumeric("YlOrRd", domain = nta_data$chinese_pct)

# Map
leaflet() %>%
  addProviderTiles("CartoDB.Positron") %>%

  # Gradient fill for % Chinese
  addPolygons(
    data = nta_data,
    fillColor = ~pal(chinese_pct),
    fillOpacity = 0.7,
    color = "#333333",
    weight = 1,
    label = ~paste0(NTAName, ": ", round(chinese_pct, 1), "% Chinese")
  ) %>%

  # L1: yellow
  addCircleMarkers(data = l1, radius = 4, color = "yellow", fillOpacity = 0.9,
                   stroke = FALSE, label = ~Business_Name, group = "L1 - Shops") %>%

  # L2: orange
  addCircleMarkers(data = l2, radius = 5, color = "orange", fillOpacity = 0.9,
                   stroke = FALSE, label = ~Business_Name, group = "L2 - Community") %>%

  # L3: red
  addCircleMarkers(data = l3, radius = 6, color = "red", fillOpacity = 0.9,
                   stroke = FALSE, label = ~Business_Name, group = "L3 - Institutions") %>%

  # Optional: Transit layers
  # addPolylines(data = mta_lines, color = "blue", weight = 2, group = "MTA") %>%
  addPolylines(data = dollar_vans, color = "blue", weight = 4, group = "Dollar Vans") %>%

  addLegend("bottomright", pal = pal, values = nta_data$chinese_pct,
            title = "% Chinese Population", opacity = 0.7) %>%

  addLayersControl(
    overlayGroups = c("L1 - Shops", "L2 - Community", "L3 - Institutions"),
    options = layersControlOptions(collapsed = FALSE)
  )

```

